\bf Nonparametric Bootstrap KS Test with Stationary Time Series

### 2023-10-10 manuscript/manuscript.tex
Figures

@@

@@

>>>>

The Kolmogorov-Smirnov (KS) statistic is widely used to test if a sample is
from a given distribution.

@@

The Kolmogorov-Smirnov (KS) test is a useful goodness-of-fit statistic. It 
can be used to see if a population follows a hypothesized distribution and has 
and can be applied to a variety of fields. It has
been used to analyze the random distribution of cosmic microwave background 
radiation \citep{naess2012application}. A common misuse of the KS test is when
the hypothesized distribution has unspecified parameters. 
\citet{babu2004goodness} approaches this scenario using basic 
non-parametric bootstrap. There is also the scenario where both the hypothesized 
distribution has unspecified parameters and additionally the data are 
serially dependent. \citet{zeimbekakis2022misuses} demonstrates a remedy for
this scenario using semi-parametric bootstrap. This study aims to address this
scenario with non-parametric block bootstrap.

The rest of the paper is outlined as follows: in the first 
section, we assess whether the KS
test holds its size; that is, does the test fail to reject the null hypothesis
when it is true. In the second section, we evaluate the 
test's power; that is, does the test reject the null hypothesis when it is 
false.
Finally, we end with 
concluding remarks in the third section.

\section{Methods}
\label{sec:methods}

Consider a stationary time series $\{X_t: t = 1, \ldots, n\}$ with length~$n$. 
Our goal is to see if the data generating model of the series matches a 
hypothesized distribution. If the observations in the series were independent, a 
standard
nonparametric bootstrap KS test would draw a large number~$B$ bootstrap copies 
of the observed data, and compute the empirical distribution and a
fitted distribution from the fitted parameters
$\hat\theta_n^{(b)}$ for each copy $b = 1, \ldots, B$. ____ When serial 
dependence is present, the bootstrap procedure 
needs to preserve the serial dependence. Block bootstrap was motivated for this 
situation.

@@

\section{Null Hypothesis}
\label{sec:null}

\section{Alternative Hypothesis}
\label{sec:alternative}
